---
title: "Assignment 4"
author: "David Lopez Amaya"
date: "2023-04-16"
output: html_document
---


1. For the state of New Mexico, generate a dataset that reports out the following variables
for the non-Hispanic white, Hispanic, and Native American: Pct. White, Pct. Hispanic,
Pct. Native, below is a list of variable from the script * indicates filler for the three race groups above.
    med_hh_inc_*,
    pct_hh_inc_*_ 100p, pct_hh_inc_*_p,
    pct_snap_*,
    pct_*_below_poverty,
    pct_*_below_poverty_child, pct_*_below_poverty_adult,
    pct_educ_less_hs_*, pct_educ_bacherlor_*,
    pct_unemployed_*,
    pct_disabled_*,
    pct_uninsure_*_19_64
    
    
Establish Source Code ACS Vars:


```{r}
acs_vars <- c(# Median HH Income #
              "B19013_001",  # Median HH Income
              
              "B01003_001",  # Total Pop
              "B03002_012",  # Hispanic/Latino
              
              # Median Household Income, Hispanic/Latino #
              "B19013I_001", # Median Hispanic/Latino
              
              # Household Income, Hispanic/Latino #
              "B19001_001",  # Income total households
              "B19001I_001", # Income total Hispanic/Latino households 
              "B19001I_014", # HH income Hispanic/Latino > 100,000 to $124,999
              "B19001I_015", # HH income Hispanic/Latino 125,000 to $149,999
              "B19001I_016", # HH income Hispanic/Latino 150,000 to $199,999
              "B19001I_017", # HH income Hispanic/Latino 200,000 or more
              
              # SNAP, Hispanic/Latino #
              "B22005I_002", # Snap Hispanic/Latino
              "B22005I_001", # Snap Hispanic/Latino Denominator  
              
              # Poverty Status, Hispanic/Latino #
              "B17001I_001", # POVERTY STATUS (Hispanic/Latino) # Denominator
              "B17001I_002", # Income Below poverty level (Hispanic/Latino)
              
              # Total Hispanic/Latino #
              "B17001I_001", # Estimate!!Total: POVERTY STATUS IN THE PAST 12 MONTHS BY SEX BY AGE (WHITE ALONE, NOT HISPANIC OR LATINO)
              
              # Poverty Status, Hispanic/Latino Men #
              "B17001I_004",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
              "B17001I_005",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
              "B17001I_006",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
              "B17001I_007",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
              "B17001I_008",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
              "B17001I_009",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
              "B17001I_010",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
              "B17001I_011",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
              "B17001I_012",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
              "B17001I_013",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
              "B17001I_014",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
              "B17001I_015",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
              "B17001I_016",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
              
              # At or Above Poverty status Hispanic/Latino Men (use this to combine with above for Denominator)
              "B17001I_033",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
              "B17001I_034",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
              "B17001I_035",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
              "B17001I_036",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
              "B17001I_037",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
              "B17001I_038",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
              "B17001I_039",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
              "B17001I_040",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
              "B17001I_041",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
              "B17001I_042",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
              "B17001I_043",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
              "B17001I_044",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
              "B17001I_045",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
              
              # Poverty Status, Hispanic/Latino Women #
              "B17001I_018",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
              "B17001I_019",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
              "B17001I_020",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
              "B17001I_021",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
              "B17001I_022",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
              "B17001I_023",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
              "B17001I_024",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
              "B17001I_025",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
              "B17001I_026",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
              "B17001I_027",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
              "B17001I_028",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
              "B17001I_029",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
              "B17001I_030",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over
              
              # At or Above Poverty status Hispanic/Latino Women (use this to combine with above for Denominator)              
              "B17001I_047",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
              "B17001I_048",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
              "B17001I_049",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
              "B17001I_050",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
              "B17001I_051",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
              "B17001I_052",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
              "B17001I_053",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
              "B17001I_054",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
              "B17001I_055",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
              "B17001I_056",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
              "B17001I_057",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
              "B17001I_058",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
              "B17001I_059",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over              
              
              # Educational Attainment, Hispanic/Latino #
              
              # Total Hispanic/Latino #
              "C15002I_001",	# Estimate!!Total:	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Hispanic/Latino Men #
              "C15002I_003",	# Estimate!!Total:!!Male:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (HISPANIC OR LATINO)
              "C15002I_006",	# Estimate!!Total:!!Male:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Hispanic/Latino Women #
              "C15002I_008",	# Estimate!!Total:!!Female:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (HISPANIC OR LATINO)
              "C15002I_011",  # Estimate!!Total:!!Female:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Employment Status, Hispanic/Latino #
              
              # Civilian Employment Status 16-64 (In labor force), Hispanic/Latino Men #
              "C23002I_006", 	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Employed vs Unemployed #
              "C23002I_008",	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Civilian Employment Status 16-64, Hispanic/Latino Women #
              "C23002I_019",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (HISPANIC OR LATINO)                
              
              # Employed vs Unemployed #
              "C23002I_021",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (HISPANIC OR LATINO)
              
              # Disability Status, Hispanic/Latino # 
              
              # Disability status, ages 18-64 Hispanic/Latino
              "B18101I_005",	# Estimate!!Total:!!18 to 64 years:	AGE BY DISABILITY STATUS (HISPANIC OR LATINO)
              "B18101I_006",	# Estimate!!Total:!!18 to 64 years:!!With a disability	AGE BY DISABILITY STATUS (HISPANIC OR LATINO)
              
              # Insurance Status, Hispanic/Latino #
              
              # Health Insurance Coverage Hispanic/Latino, by Age #
              "C27001I_001",	# Estimate!!Total:	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_002",	# Estimate!!Total:!!Under 19 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_004",	# Estimate!!Total:!!Under 19 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_005",	# Estimate!!Total:!!19 to 64 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_007",	# Estimate!!Total:!!19 to 64 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_008",	# Estimate!!Total:!!65 years and over:	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)
              "C27001I_010",	# Estimate!!Total:!!65 years and over:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (HISPANIC OR LATINO)

              "B01003_001",  # Total Pop
              "B03002_005",   # Native
              
              # Median Household Income, Native #
              "B19013C_001", # Median White alone Native
              
              # Household Income, White #
              "B19001_001",  # Income total households
              "B19001C_001", # Income total white households 
              "B19001C_014", # HH income Native > 100,000 to $124,999
              "B19001C_015", # HH income Native 125,000 to $149,999
              "B19001C_016", # HH income Native 150,000 to $199,999
              "B19001C_017", # HH income Native 200,000 or more
              
              # SNAP, Native #
              "B22005C_002", # Snap Native
              "B22005C_001", # Snap Native Denominator 
              
              # Poverty Status, Native # 
              "B17001C_001", # POVERTY STATUS (Native) # Denominator
              "B17001C_002", # Income Below poverty level (Native)
              
              # Total Native #
              "B17001C_001", # Estimate!!Total: POVERTY STATUS IN THE PAST 12 MONTHS BY SEX BY AGE (NATIVE)
              
              # Poverty Status, Native Men #
              "B17001C_004",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
              "B17001C_005",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
              "B17001C_006",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
              "B17001C_007",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
              "B17001C_008",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
              "B17001C_009",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
              "B17001C_010",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
              "B17001C_011",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
              "B17001C_012",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
              "B17001C_013",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
              "B17001C_014",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
              "B17001C_015",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
              "B17001C_016",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
              
              # At or Above Poverty status Native Men (use this to combine with above for Denominator)
              "B17001C_032",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:
              "B17001C_033",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
              "B17001C_034",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
              "B17001C_035",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
              "B17001C_036",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
              "B17001C_037",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
              "B17001C_038",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
              "B17001C_039",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
              "B17001C_040",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
              "B17001C_041",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
              "B17001C_042",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
              "B17001C_043",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
              "B17001C_044",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
              "B17001C_045",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
              
              # Poverty Status, Native Women #
              "B17001C_018",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
              "B17001C_019",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
              "B17001C_020",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
              "B17001C_021",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
              "B17001C_022",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
              "B17001C_023",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
              "B17001C_024",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
              "B17001C_025",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
              "B17001C_026",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
              "B17001C_027",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
              "B17001C_028",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
              "B17001C_029",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
              "B17001C_030",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over
              
              # At or Above Poverty status Native Women (use this to combine with above for Denominator)
              "B17001C_047",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
              "B17001C_048",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
              "B17001C_049",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
              "B17001C_050",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
              "B17001C_051",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
              "B17001C_052",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
              "B17001C_053",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
              "B17001C_054",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
              "B17001C_055",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
              "B17001C_056",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
              "B17001C_057",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
              "B17001C_058",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
              "B17001C_059",  #Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over
              
              # Educational Attainment, Native #
              
              # Total Native #
              "C15002C_001",	# Estimate!!Total:	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (Native)
              
              # Native Men #
              "C15002C_003",	# Estimate!!Total:!!Male:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (Native)
              "C15002C_006",	# Estimate!!Total:!!Male:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (Native)
              
              # Native Women #
              "C15002C_008",	# Estimate!!Total:!!Female:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (Native)
              "C15002C_011",  # Estimate!!Total:!!Female:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (Native)
              
              # Employment Status, Native #
              
              # Civilian Employment Status 16-64 (In labor force), Native Men #
              "C23002C_006", 	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (Native)
              
              # Employed vs Unemployed #
              "C23002C_008",	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (Native)
              
              # Civilian Employment Status 16-64, Native Women #
              "C23002C_019",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (Native)                
              
              # Employed vs Unemployed #
              "C23002C_021",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (Native)
              
              # Disability Status, Native # 
              
              # Disability status, ages 18-64 Native
              "B18101C_005",	# Estimate!!Total:!!18 to 64 years:	AGE BY DISABILITY STATUS (NATIVE)
              "B18101C_006",	# Estimate!!Total:!!18 to 64 years:!!With a disability	AGE BY DISABILITY STATUS (NATIVE)
              
              # Insurance Status, Native #
              
              # Health Insurance Coverage Native, by Age #
              "C27001C_001",	# Estimate!!Total:	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_002",	# Estimate!!Total:!!Under 19 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_004",	# Estimate!!Total:!!Under 19 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_005",	# Estimate!!Total:!!19 to 64 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_007",	# Estimate!!Total:!!19 to 64 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_008",	# Estimate!!Total:!!65 years and over:	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)
              "C27001C_010",	# Estimate!!Total:!!65 years and over:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (Native)

              "B01003_001",  # Total Pop
              "B03002_003",  # White NH
              
              # Median Household Income, White #
              "B19013H_001", # Median White alone NH
              
              # Household Income, White #
              "B19001_001",  # Income total households
              "B19001H_001", # Income total white households 
              "B19001H_014", # HH income white > 100,000 to $124,999
              "B19001H_015", # HH income white 125,000 to $149,999
              "B19001H_016", # HH income white 150,000 to $199,999
              "B19001H_017", # HH income white 200,000 or more
              
              # SNAP, White #
              "B22005H_002", # Snap White
              "B22005H_001", # Snap White Denominator 
              
              # Poverty Status, White # 
              "B17001H_001", # POVERTY STATUS (NH White) # Denominator
              "B17001H_002", # Income Below poverty level (White)
              
              # Total White #
              "B17001H_001", # Estimate!!Total: POVERTY STATUS IN THE PAST 12 MONTHS BY SEX BY AGE (WHITE ALONE, NOT HISPANIC OR LATINO)
              
              # Poverty Status, White Men #
              "B17001H_004",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
              "B17001H_005",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
              "B17001H_006",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
              "B17001H_007",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
              "B17001H_008",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
              "B17001H_009",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
              "B17001H_010",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
              "B17001H_011",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
              "B17001H_012",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
              "B17001H_013",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
              "B17001H_014",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
              "B17001H_015",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
              "B17001H_016",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
              
              # At or Above Poverty status White Men (use this to combine with above for Denominator)
              "B17001H_032",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:
              "B17001H_033",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
              "B17001H_034",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
              "B17001H_035",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
              "B17001H_036",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
              "B17001H_037",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
              "B17001H_038",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
              "B17001H_039",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
              "B17001H_040",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
              "B17001H_041",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
              "B17001H_042",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
              "B17001H_043",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
              "B17001H_044",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
              "B17001H_045",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
              
              # Poverty Status, White Women #
              "B17001H_018",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
              "B17001H_019",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
              "B17001H_020",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
              "B17001H_021",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
              "B17001H_022",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
              "B17001H_023",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
              "B17001H_024",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
              "B17001H_025",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
              "B17001H_026",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
              "B17001H_027",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
              "B17001H_028",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
              "B17001H_029",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
              "B17001H_030",	# Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over
              
              # At or Above Poverty status White Women (use this to combine with above for Denominator)
              "B17001H_047",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
              "B17001H_048",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
              "B17001H_049",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
              "B17001H_050",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
              "B17001H_051",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
              "B17001H_052",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
              "B17001H_053",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
              "B17001H_054",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
              "B17001H_055",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
              "B17001H_056",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
              "B17001H_057",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
              "B17001H_058",	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
              "B17001H_059",  	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over
              
              # Educational Attainment, White #
              
              # Total White #
              "C15002H_001",	# Estimate!!Total:	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (White NH)
              
              # White Men #
              "C15002H_003",	# Estimate!!Total:!!Male:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (White NH)
              "C15002H_006",	# Estimate!!Total:!!Male:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (White NH)
              
              # White Women #
              "C15002H_008",	# Estimate!!Total:!!Female:!!Less than high school diploma	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (White NH)
              "C15002H_011",  # Estimate!!Total:!!Female:!!Bachelor's degree or higher	SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER (White NH)
              
              # Employment Status, White #
              
              # Civilian Employment Status 16-64 (In labor force), White Men #
              "C23002H_006", 	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (White Not HS)
              
              # Employed vs Unemployed #
              "C23002H_008",	# Estimate!!Total:!!Male:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (White Not HS)
              
              # Civilian Employment Status 16-64, White Women #
              "C23002H_019",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (White Not HS)                
              
              # Employed vs Unemployed #
              "C23002H_021",	# Estimate!!Total:!!Female:!!16 to 64 years:!!In labor force:!!Civilian:!!Unemployed	SEX BY AGE BY EMPLOYMENT STATUS FOR THE POPULATION 16 YEARS AND OVER (White Not HS)
              
              # Disability Status, White # 
              
              # Disability status, ages 18-64 White
              "B18101H_005",	# Estimate!!Total:!!18 to 64 years:	AGE BY DISABILITY STATUS (WHITE ALONE, NOT HISPANIC OR LATINO)
              "B18101H_006",	# Estimate!!Total:!!18 to 64 years:!!With a disability	AGE BY DISABILITY STATUS (WHITE ALONE, NOT HISPANIC OR LATINO)
              
              # Insurance Status, White #
              
              # Health Insurance Coverage White, by Age #
              "C27001H_001",	# Estimate!!Total:	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_002",	# Estimate!!Total:!!Under 19 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_004",	# Estimate!!Total:!!Under 19 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_005",	# Estimate!!Total:!!19 to 64 years:	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_007",	# Estimate!!Total:!!19 to 64 years:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_008",	# Estimate!!Total:!!65 years and over:	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
              "C27001H_010"	# Estimate!!Total:!!65 years and over:!!No health insurance coverage	HEALTH INSURANCE COVERAGE STATUS BY AGE (White NH)
)
```


2. Produce a table with the results, showing the share of Hispanic, nh-White, Native
American, respectively, that fill out the categories. For example, what percentage of
white households receive SNAP? In a paragraph discuss the main findings.

Generate Table for NM:


```{r}
rm(list=ls())

# Packages #
library(tigris)
library(tidycensus)
library(tidyverse)
library(dplyr)
library(haven)
library(reactable)
key = "4e29c959c64c919e7df032a5fed2ae4b8b88eee8"
census_api_key(key)

# Source Code #
source("C:/Users/dalop/Dropbox/pols512/assignment_4/acs_vars.R")

acs_factor5 <- function(vars, # Make individual vectors for each racial group #
                        geography = "state",
                        year = 2020,        
                        state){
  
  acs20_state <- get_acs(geography = geography, 
                         variables = acs_vars, 
                         year = year,
                         state = state,
                         output = "wide")
  
  acs20_state_final <- acs20_state %>%
    mutate(tot_pop= B01003_001E,
           
           # Race/Ethnicity #
           nh_white= B03002_003E,
           nh_native= B03002_005E, 
           hispanic= B03002_012E, 
           pct_white = nh_white / tot_pop, 
           pct_native = nh_native /tot_pop, 
           pct_hispanic = hispanic / tot_pop,
           
           # Median HH Income #
           med_hh_inc= B19013_001E, 
           med_hh_inc_white = B19013H_001E, 
           med_hh_inc_native = B19013C_001E, 
           med_hh_inc_hispanic = B19013I_001E, 
           
           # Household Income #
           inc_total_households = B19001_001E, 
           inc_total_households_white = B19001H_001E,
           inc_total_households_native = B19001C_001E, 
           inc_total_households_hispanic = B19001I_001E, 
           hh_inc_total_white_100 =B19001H_014E, 
           hh_inc_total_white_125 =B19001H_015E, 
           hh_inc_total_white_150 =B19001H_016E, 
           hh_inc_total_white_200 = B19001H_017E, 
           hh_inc_total_native_100 = B19001C_014E, 
           hh_inc_total_native_125 = B19001C_015E, 
           hh_inc_total_native_150 = B19001C_016E, 
           hh_inc_total_native_200 = B19001C_017E,
           hh_inc_total_hispanic_100 = B19001I_014E, 
           hh_inc_total_hispanic_125 = B19001I_015E, 
           hh_inc_total_hispanic_150 = B19001I_016E, 
           hh_inc_total_hispanic_200 = B19001I_017E,
           pct_hh_inc_white_100p= (hh_inc_total_white_100 + hh_inc_total_white_125 + 
                                     hh_inc_total_white_150+ 
                                     hh_inc_total_white_200)/inc_total_households_white, 
           pct_hh_inc_white_125p= (hh_inc_total_white_125 + hh_inc_total_white_150+
                                     hh_inc_total_white_200)/inc_total_households_white, 
           pct_hh_inc_native_100p= (hh_inc_total_native_100 + hh_inc_total_native_125 + 
                                     hh_inc_total_native_150+ 
                                     hh_inc_total_native_200)/inc_total_households_native, 
           pct_hh_inc_native_125p= (hh_inc_total_native_125 + hh_inc_total_native_150+ 
                                     hh_inc_total_native_200)/inc_total_households_native, 
           pct_hh_inc_hispanic_100p= (hh_inc_total_hispanic_100 + hh_inc_total_hispanic_125 + 
                                      hh_inc_total_hispanic_150+ 
                                      hh_inc_total_hispanic_200)/inc_total_households_hispanic, 
           pct_hh_inc_hispanic_125p= (hh_inc_total_hispanic_125 + hh_inc_total_hispanic_150+ 
                                      hh_inc_total_hispanic_200)/inc_total_households_hispanic, 
           
           # SNAP #
           snap_white= B22005H_002E, 
           snap_native= B22005C_002E,
           snap_hispanic= B22005I_002E,
           pct_snap_white= snap_white/B22005H_001E,
           pct_snap_native= snap_native/B22005C_001E, 
           pct_snap_hispanic= snap_hispanic/B22005I_001E,
           
           # Poverty Status 
           pct_white_below_poverty = B17001H_002E / B17001H_001E,
           pct_native_below_poverty = B17001C_002E / B17001C_001E,
           pct_hispanic_below_poverty = B17001I_002E / B17001I_001E,
           
           # Poverty Status White Below 18 #
           white_below18_total = B17001H_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001H_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001H_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001H_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001H_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001H_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001H_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001H_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001H_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001H_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001H_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001H_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001H_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001H_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001H_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001H_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001H_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001H_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001H_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001H_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001H_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001H_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001H_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001H_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
             
           white_below18_poverty = B17001H_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001H_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001H_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001H_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001H_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001H_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001H_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001H_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001H_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001H_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001H_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001H_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
           
           pct_white_below_poverty_child = white_below18_poverty / white_below18_total,
           
           # Poverty Status White Adults #
           white_above18_total = B17001H_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001H_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001H_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001H_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001H_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001H_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001H_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001H_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001H_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001H_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001H_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001H_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001H_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
             B17001H_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001H_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001H_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001H_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001H_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001H_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001H_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001H_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001H_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001H_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001H_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001H_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001H_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001H_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over              
             
           white_above18_poverty = B17001H_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001H_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001H_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001H_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001H_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001H_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001H_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001H_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001H_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001H_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001H_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001H_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001H_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001H_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over  
           
           pct_white_below_poverty_adult = white_above18_poverty /white_above18_total,
           
           # Poverty Status Native Below 18 #
           native_below18_total = B17001C_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001C_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001C_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001C_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001C_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001C_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001C_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001C_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001C_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001C_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001C_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001C_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001C_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001C_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001C_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001C_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001C_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001C_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001C_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001C_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001C_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001C_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001C_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001C_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
             
           native_below18_poverty = B17001C_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001C_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001C_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001C_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001C_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001C_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001C_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001C_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001C_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001C_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001C_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001C_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
           
           pct_native_below_poverty_child = native_below18_poverty / native_below18_total,
           
           # Poverty Status Native Adults #
           native_above18_total = B17001C_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001C_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001C_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001C_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001C_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001C_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001C_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001C_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001C_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001C_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001C_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001C_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001C_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001C_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over 
             B17001C_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001C_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001C_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001C_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001C_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001C_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001C_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001C_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001C_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001C_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001C_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001C_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001C_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001C_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over            
          
           native_above18_poverty = B17001C_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001C_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001C_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001C_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001C_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001C_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001C_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001C_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001C_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001C_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001C_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001C_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001C_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001C_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
           
           pct_native_below_poverty_adult = native_above18_poverty / native_above18_total,
           
           # Poverty Status Hispanic Below 18 #
           hispanic_below18_total = B17001I_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001I_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001I_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001I_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001I_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001I_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001I_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001I_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001I_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001I_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001I_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001I_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001I_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001I_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001I_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001I_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001I_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001I_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001I_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001I_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001I_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001I_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001I_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001I_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
             
           hispanic_below18_poverty = B17001I_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001I_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001I_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001I_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001I_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001I_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001I_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001I_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001I_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001I_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001I_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001I_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
          
           pct_hispanic_below_poverty_child = hispanic_below18_poverty / hispanic_below18_total,
           
           # Poverty Status Hispanic Adults #
           hispanic_above18_total = B17001I_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001I_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001I_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001I_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001I_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001I_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001I_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001I_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001I_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001I_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001I_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001I_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001I_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001I_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
             B17001I_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001I_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001I_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001I_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001I_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001I_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001I_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001I_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001I_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001I_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001I_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001I_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001I_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001I_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over              
             
           hispanic_above18_poverty = B17001I_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001I_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001I_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001I_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001I_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001I_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001I_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001I_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001I_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001I_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001I_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001I_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001I_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001I_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over  
           
           pct_hispanic_below_poverty_adult = hispanic_above18_poverty / hispanic_above18_total,
           
           #Educational Attainment, White #
           pct_educ_less_hs_white = (C15002H_003E + C15002H_008E)/C15002H_001E,
           pct_educ_bachelor_white= (C15002H_006E+ C15002H_011E)/C15002H_001E,
          
           #Educational Attainment, Native #
           pct_educ_less_hs_native = (C15002C_003E + C15002C_008E)/C15002C_001E,
           pct_educ_bachelor_native= (C15002C_006E+ C15002C_011E)/C15002C_001E, 
           
           #Educational Attainment, Hispanic #
           pct_educ_less_hs_hispanic = (C15002I_003E + C15002I_008E)/C15002I_001E,
           pct_educ_bachelor_hispanic= (C15002I_006E+ C15002I_011E)/C15002I_001E,
           
           #Civilian Employment in Labor Force, 16-64 White
           civilian_empl_status_total_white= C23002H_006E+ C23002H_019E,
           pct_umemployed_white = (C23002H_008E+C23002H_021E)/civilian_empl_status_total_white,
           
           #Civilian Employment in Labor Force, 16-64 Native
           civilian_empl_status_total_native= C23002C_006E+ C23002C_019E,
           pct_umemployed_native = (C23002C_008E+C23002C_021E)/civilian_empl_status_total_native,
           
           #Civilian Employment in Labor Force, 16-64 Hispanic
           civilian_empl_status_total_hispanic= C23002I_006E+ C23002I_019E,
           pct_umemployed_hispanic = (C23002I_008E+C23002I_021E)/civilian_empl_status_total_hispanic,
           
           #Disabled, Ages 18-64 White, Native, Hispanic
           pct_disabled_white= B18101H_006E/B18101H_005E, 
           pct_disabled_native= B18101C_006E/B18101C_005E,
           pct_disabled_hispanic= B18101I_006E/B18101I_005E,
           
           #Uninsured White, Native, Hispanic (19-64)
           pct_uninsured_white_19_64 = C27001H_007E/C27001H_005E,
           pct_uninsured_native_19_64 = C27001C_007E/C27001C_005E, 
           pct_uninsured_hispanic_19_64 = C27001I_007E/C27001I_005E
    ) %>% select(pct_white, pct_native, pct_hispanic,
                 med_hh_inc_white, med_hh_inc_native, med_hh_inc_hispanic,
                 pct_hh_inc_white_100p, pct_hh_inc_white_125p,
                 pct_hh_inc_native_100p, pct_hh_inc_native_125p,
                 pct_hh_inc_hispanic_100p, pct_hh_inc_hispanic_125p, 
                 pct_snap_white, pct_snap_native, pct_snap_hispanic,
                 pct_white_below_poverty, pct_native_below_poverty, pct_hispanic_below_poverty,
                 pct_white_below_poverty_child, pct_white_below_poverty_adult, 
                 pct_native_below_poverty_child, pct_native_below_poverty_adult,
                 pct_hispanic_below_poverty_child, pct_hispanic_below_poverty_adult, 
                 pct_educ_less_hs_white, pct_educ_bachelor_white, 
                 pct_educ_less_hs_native, pct_educ_bachelor_native,
                 pct_educ_less_hs_hispanic, pct_educ_bachelor_hispanic, 
                 pct_umemployed_white, pct_umemployed_native, pct_umemployed_hispanic,
                 pct_disabled_white, pct_disabled_native, pct_disabled_hispanic,
                 pct_uninsured_white_19_64, pct_uninsured_native_19_64, pct_uninsured_hispanic_19_64)
  
  # Write out #
  write_rds(acs20_state_final, 
            file ="nm_acs20_state_final.rds")      
  
  # Turn the above into a function with a write out option -- then apply the function to the county  data
  # County #
  acs20_county <- get_acs(geography = "county", 
                          variables = acs_vars, 
                          year = 2020,
                          state = "NM", output="wide")
  
  # White Vector #
  white <- acs20_state_final %>%
    select(med_hh_inc_white,
           pct_hh_inc_white_100p,
           pct_hh_inc_white_125p,
           pct_snap_white,
           pct_white_below_poverty,
           pct_white_below_poverty_child,
           pct_white_below_poverty_adult,
           pct_educ_less_hs_white, 
           pct_educ_bachelor_white,
           pct_umemployed_white,
           pct_disabled_white,
           pct_uninsured_white_19_64)
  
  # Native Vector #
  native <- acs20_state_final %>%
    select(med_hh_inc_native, 
           pct_hh_inc_native_100p,
           pct_hh_inc_native_125p,
           pct_snap_native,
           pct_native_below_poverty,
           pct_native_below_poverty_child,
           pct_native_below_poverty_adult,
           pct_educ_less_hs_native,
           pct_educ_bachelor_native,
           pct_umemployed_native,
           pct_disabled_native,
           pct_uninsured_native_19_64) 
  
  # Hispanic Vector #
  hispanic <- acs20_state_final %>%
    select(med_hh_inc_hispanic,
           pct_hh_inc_hispanic_100p,
           pct_hh_inc_hispanic_125p,
           pct_snap_hispanic,
           pct_hispanic_below_poverty,
           pct_hispanic_below_poverty_child,
           pct_hispanic_below_poverty_adult,
           pct_educ_less_hs_hispanic, 
           pct_educ_bachelor_hispanic,
           pct_umemployed_hispanic,
           pct_disabled_hispanic,
           pct_uninsured_hispanic_19_64)
  
  # Combine Data #
  ses <- data.frame(White = round(t(white), 3),
                    Native = round(t(native),3),
                    Hispanic = round(t(hispanic),3)) %>%
    dplyr::mutate(White_NativeDiff = White - Native) %>%
    dplyr::mutate(White_HispanicDiff = White - Hispanic) %>%
    dplyr::mutate(Hispanic_NativeDiff = Hispanic - Native)
  
  # Recode Adjustments #
  ses$White[1] <- paste0("$",ses$White[1])
  ses$Native[1] <- paste0("$",ses$Native[1])
  ses$Hispanic[1] <- paste0("$",ses$Hispanic[1])
  ses$White_NativeDiff[1] <- paste0("$",ses$White_NativeDiff[1])
  ses$White_HispanicDiff[1] <- paste0("$",ses$White_HispanicDiff[1])
  ses$Hispanic_NativeDiff[1] <- paste0("$",ses$Hispanic_NativeDiff[1])
  
  # Table Labeling #
  colnames(ses) <- c("White", "Native", "Hispanic", "White - Native", "White - Hispanic", "Hispanic - Native")
  
  rownames(ses) <- c("Median Household Income",
                     "Pct. HH Income > $100K",
                     "Pct. HH Income > $125K",
                     "Pct. HH receiving SNAP",
                     "Pct. HH below poverty line",
                     "Pct. HH below poverty line, children",
                     "Pct. HH below poverty line, VAP",
                     "Pct. w/ Less than HS Diploma",
                     "Pct. w/ Bachelor's Degree or higher",
                     "Pct. Unemployed",
                     "Pct Disabled, ages 19-64",
                     "Pct. Uninsured, ages 19-64"
  )
  
  # Produce Table -- as an exmaple #
  reactable(ses,
            pagination = F,
            width = 700)
  
}

# Execute #
acs_factor5(vars = acs_vars,
            state = "NM")
```

Main Findings:

In the state of New Mexico, Non-Hispanic White residents are the highest median household income earners of the three racial/ethnic groups analyzed, with a median household income of $60,767. White residents of the state make $24,472 more than their Native American counterparts and $16,119 more than their Hispanic/Latino counterparts respectively. Both minority groups (Native Americans and Hispanics/Latinos), heavily depend on public assistance, with 29.8% of Native American household and 22.4% of Hispanic households relying on SNAP assistance compared to only 10% of Non-Hispanic White households. Native Americans also tend to experience high levels of poverty, particularly those aged 0-17 years old, with 40.3% of Native American youth living below the poverty line; despite poverty decreasing in age groups above the aforementioned range, adult poverty for this particular racial group remains above the 25% threshold. Non-Hispanic Whites are the most highly educated racial group in the state, with 41% of Non-Hispanic Whites having a Bachelor's Degree or higher, in sharp contrast, Hispanics/Latinos are the largest group with an education level lower than a high school diploma, 21%. However, unemployment for these groups are relatively similar, with 5% of Non-Hispanic Whites and 6% of Hispanic/Latinos being unemployed. Similarly, both these groups share identical rates of disability with 13.6% of Non-Hispanic Whites and Hispanics/Latinos being disabled. Native Americans are the least insured demographic with 26.8% of the population being uninsured, a 19% difference when compared to their Non-Hispanic White counterparts. 


3. Write a function that calls the ACS data, specifies race group (focusing on either NH-
White, NH-Black, Native American, AAPI, Hispanic) as the main possible groups, then
spits out a table comparison. Also include arguments for the types of variables to
include (ie., HH Income, Snap). The function should take all variables I produced in class
as the default but allow the user to specify a subset of variables. Test out the function
with New Mexico data, then use it to collect California data. Produce a table just for CA,
including the above race populations (since there are probably just enough in all groups
for useful comparisons). Consider sizing options for the table so that it is readable.

```{r}


rm(list=ls())

# Packages #
library(tigris)
library(tidycensus)
library(tidyverse)
library(dplyr)
library(haven)
library(reactable)
key = "4e29c959c64c919e7df032a5fed2ae4b8b88eee8"
census_api_key(key)

# Source Code #
source("C:/Users/dalop/Dropbox/pols512/assignment_4/acs_vars.R")

#acs_factor5(vars = c("B19013_001", "B01003_001", "B03002_012")) Change variables as needed

acs_factor5 <- function(vars, # Make individual vectors for each racial group #
                        geography = "state",
                        year = 2020,        
                        state){
  
  acs20_state <- get_acs(geography = geography, 
                         variables = acs_vars, 
                         year = year,
                         state = state,
                         output = "wide")
  
  acs20_state_final <- acs20_state %>%
    mutate(tot_pop= B01003_001E,
           
           # Race/Ethnicity #
           nh_white= B03002_003E,
           nh_native= B03002_005E, 
           hispanic= B03002_012E, 
           pct_white = nh_white / tot_pop, 
           pct_native = nh_native /tot_pop, 
           pct_hispanic = hispanic / tot_pop,
           
           # Median HH Income #
           med_hh_inc= B19013_001E, 
           med_hh_inc_white = B19013H_001E, 
           med_hh_inc_native = B19013C_001E, 
           med_hh_inc_hispanic = B19013I_001E, 
           
           # Household Income #
           inc_total_households = B19001_001E, 
           inc_total_households_white = B19001H_001E,
           inc_total_households_native = B19001C_001E, 
           inc_total_households_hispanic = B19001I_001E, 
           hh_inc_total_white_100 =B19001H_014E, 
           hh_inc_total_white_125 =B19001H_015E, 
           hh_inc_total_white_150 =B19001H_016E, 
           hh_inc_total_white_200 = B19001H_017E, 
           hh_inc_total_native_100 = B19001C_014E, 
           hh_inc_total_native_125 = B19001C_015E, 
           hh_inc_total_native_150 = B19001C_016E, 
           hh_inc_total_native_200 = B19001C_017E,
           hh_inc_total_hispanic_100 = B19001I_014E, 
           hh_inc_total_hispanic_125 = B19001I_015E, 
           hh_inc_total_hispanic_150 = B19001I_016E, 
           hh_inc_total_hispanic_200 = B19001I_017E,
           pct_hh_inc_white_100p= (hh_inc_total_white_100 + hh_inc_total_white_125 + 
                                     hh_inc_total_white_150+ 
                                     hh_inc_total_white_200)/inc_total_households_white, 
           pct_hh_inc_white_125p= (hh_inc_total_white_125 + hh_inc_total_white_150+
                                     hh_inc_total_white_200)/inc_total_households_white, 
           pct_hh_inc_native_100p= (hh_inc_total_native_100 + hh_inc_total_native_125 + 
                                      hh_inc_total_native_150+ 
                                      hh_inc_total_native_200)/inc_total_households_native, 
           pct_hh_inc_native_125p= (hh_inc_total_native_125 + hh_inc_total_native_150+ 
                                      hh_inc_total_native_200)/inc_total_households_native, 
           pct_hh_inc_hispanic_100p= (hh_inc_total_hispanic_100 + hh_inc_total_hispanic_125 + 
                                        hh_inc_total_hispanic_150+ 
                                        hh_inc_total_hispanic_200)/inc_total_households_hispanic, 
           pct_hh_inc_hispanic_125p= (hh_inc_total_hispanic_125 + hh_inc_total_hispanic_150+ 
                                        hh_inc_total_hispanic_200)/inc_total_households_hispanic, 
           
           # SNAP #
           snap_white= B22005H_002E, 
           snap_native= B22005C_002E,
           snap_hispanic= B22005I_002E,
           pct_snap_white= snap_white/B22005H_001E,
           pct_snap_native= snap_native/B22005C_001E, 
           pct_snap_hispanic= snap_hispanic/B22005I_001E,
           
           # Poverty Status 
           pct_white_below_poverty = B17001H_002E / B17001H_001E,
           pct_native_below_poverty = B17001C_002E / B17001C_001E,
           pct_hispanic_below_poverty = B17001I_002E / B17001I_001E,
           
           # Poverty Status White Below 18 #
           white_below18_total = B17001H_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001H_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001H_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001H_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001H_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001H_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001H_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001H_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001H_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001H_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001H_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001H_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001H_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001H_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001H_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001H_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001H_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001H_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001H_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001H_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001H_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001H_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001H_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001H_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
           
           white_below18_poverty = B17001H_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001H_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001H_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001H_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001H_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001H_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001H_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001H_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001H_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001H_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001H_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001H_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
           
           pct_white_below_poverty_child = white_below18_poverty / white_below18_total,
           
           # Poverty Status White Adults #
           white_above18_total = B17001H_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001H_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001H_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001H_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001H_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001H_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001H_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001H_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001H_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001H_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001H_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001H_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001H_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
             B17001H_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001H_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001H_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001H_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001H_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001H_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001H_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001H_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001H_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001H_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001H_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001H_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001H_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001H_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over              
           
           white_above18_poverty = B17001H_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001H_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001H_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001H_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001H_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001H_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001H_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001H_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001H_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001H_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001H_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001H_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001H_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001H_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over  
           
           pct_white_below_poverty_adult = white_above18_poverty /white_above18_total,
           
           # Poverty Status Native Below 18 #
           native_below18_total = B17001C_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001C_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001C_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001C_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001C_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001C_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001C_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001C_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001C_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001C_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001C_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001C_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001C_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001C_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001C_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001C_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001C_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001C_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001C_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001C_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001C_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001C_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001C_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001C_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
           
           native_below18_poverty = B17001C_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001C_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001C_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001C_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001C_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001C_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001C_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001C_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001C_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001C_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001C_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001C_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
           
           pct_native_below_poverty_child = native_below18_poverty / native_below18_total,
           
           # Poverty Status Native Adults #
           native_above18_total = B17001C_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001C_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001C_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001C_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001C_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001C_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001C_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001C_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001C_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001C_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001C_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001C_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001C_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001C_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over 
             B17001C_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001C_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001C_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001C_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001C_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001C_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001C_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001C_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001C_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001C_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001C_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001C_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001C_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001C_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over            
           
           native_above18_poverty = B17001C_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001C_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001C_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001C_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001C_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001C_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001C_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001C_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001C_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001C_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001C_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001C_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001C_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001C_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
           
           pct_native_below_poverty_adult = native_above18_poverty / native_above18_total,
           
           # Poverty Status Hispanic Below 18 #
           hispanic_below18_total = B17001I_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001I_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001I_006E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001I_007E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001I_008E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001I_009E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001I_018E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001I_019E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001I_020E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001I_021E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001I_022E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001I_023E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
             B17001I_033E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!Under 5 years
             B17001I_034E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!5 years
             B17001I_035E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!6 to 11 years
             B17001I_036E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!12 to 14 years
             B17001I_037E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!15 years
             B17001I_038E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!16 and 17 years
             B17001I_047E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!Under 5 years
             B17001I_048E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!5 years
             B17001I_049E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!6 to 11 years
             B17001I_050E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!12 to 14 years
             B17001I_051E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!15 years
             B17001I_052E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!16 and 17 years
           
           hispanic_below18_poverty = B17001I_004E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!Under 5 years
             B17001I_005E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!5 years
             B17001I_006E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!6 to 11 years
             B17001I_007E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!12 to 14 years
             B17001I_008E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!15 years
             B17001I_009E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!16 and 17 years
             B17001I_018E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!Under 5 years
             B17001I_019E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!5 years
             B17001I_020E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!6 to 11 years
             B17001I_021E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!12 to 14 years
             B17001I_022E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!15 years
             B17001I_023E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!16 and 17 years
           
           pct_hispanic_below_poverty_child = hispanic_below18_poverty / hispanic_below18_total,
           
           # Poverty Status Hispanic Adults #
           hispanic_above18_total = B17001I_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001I_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001I_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001I_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001I_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001I_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001I_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001I_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001I_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001I_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001I_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001I_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001I_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001I_030E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over              
             B17001I_039E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!18 to 24 years
             B17001I_040E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!25 to 34 years
             B17001I_041E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!35 to 44 years
             B17001I_042E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!45 to 54 years
             B17001I_043E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!55 to 64 years
             B17001I_044E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!65 to 74 years
             B17001I_045E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Male:!!75 years and over
             B17001I_053E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!18 to 24 years
             B17001I_054E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!25 to 34 years
             B17001I_055E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!35 to 44 years
             B17001I_056E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!45 to 54 years
             B17001I_057E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!55 to 64 years
             B17001I_058E+	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!65 to 74 years
             B17001I_059E,	#Estimate!!Total:!!Income in the past 12 months at or above poverty level:!!Female:!!75 years and over              
           
           hispanic_above18_poverty = B17001I_010E +	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!18 to 24 years
             B17001I_011E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!25 to 34 years
             B17001I_012E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!35 to 44 years
             B17001I_013E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!45 to 54 years
             B17001I_014E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!55 to 64 years
             B17001I_015E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!65 to 74 years
             B17001I_016E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Male:!!75 years and over
             B17001I_024E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!18 to 24 years
             B17001I_025E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!25 to 34 years
             B17001I_026E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!35 to 44 years
             B17001I_027E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!45 to 54 years
             B17001I_028E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!55 to 64 years
             B17001I_029E+	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!65 to 74 years
             B17001I_030E,	#Estimate!!Total:!!Income in the past 12 months below poverty level:!!Female:!!75 years and over  
           
           pct_hispanic_below_poverty_adult = hispanic_above18_poverty / hispanic_above18_total,
           
           #Educational Attainment, White #
           pct_educ_less_hs_white = (C15002H_003E + C15002H_008E)/C15002H_001E,
           pct_educ_bachelor_white= (C15002H_006E+ C15002H_011E)/C15002H_001E,
           
           #Educational Attainment, Native #
           pct_educ_less_hs_native = (C15002C_003E + C15002C_008E)/C15002C_001E,
           pct_educ_bachelor_native= (C15002C_006E+ C15002C_011E)/C15002C_001E, 
           
           #Educational Attainment, Hispanic #
           pct_educ_less_hs_hispanic = (C15002I_003E + C15002I_008E)/C15002I_001E,
           pct_educ_bachelor_hispanic= (C15002I_006E+ C15002I_011E)/C15002I_001E,
           
           #Civilian Employment in Labor Force, 16-64 White
           civilian_empl_status_total_white= C23002H_006E+ C23002H_019E,
           pct_umemployed_white = (C23002H_008E+C23002H_021E)/civilian_empl_status_total_white,
           
           #Civilian Employment in Labor Force, 16-64 Native
           civilian_empl_status_total_native= C23002C_006E+ C23002C_019E,
           pct_umemployed_native = (C23002C_008E+C23002C_021E)/civilian_empl_status_total_native,
           
           #Civilian Employment in Labor Force, 16-64 Hispanic
           civilian_empl_status_total_hispanic= C23002I_006E+ C23002I_019E,
           pct_umemployed_hispanic = (C23002I_008E+C23002I_021E)/civilian_empl_status_total_hispanic,
           
           #Disabled, Ages 18-64 White, Native, Hispanic
           pct_disabled_white= B18101H_006E/B18101H_005E, 
           pct_disabled_native= B18101C_006E/B18101C_005E,
           pct_disabled_hispanic= B18101I_006E/B18101I_005E,
           
           #Uninsured White, Native, Hispanic (19-64)
           pct_uninsured_white_19_64 = C27001H_007E/C27001H_005E,
           pct_uninsured_native_19_64 = C27001C_007E/C27001C_005E, 
           pct_uninsured_hispanic_19_64 = C27001I_007E/C27001I_005E
    ) %>% select(pct_white, pct_native, pct_hispanic,
                 med_hh_inc_white, med_hh_inc_native, med_hh_inc_hispanic,
                 pct_hh_inc_white_100p, pct_hh_inc_white_125p,
                 pct_hh_inc_native_100p, pct_hh_inc_native_125p,
                 pct_hh_inc_hispanic_100p, pct_hh_inc_hispanic_125p, 
                 pct_snap_white, pct_snap_native, pct_snap_hispanic,
                 pct_white_below_poverty, pct_native_below_poverty, pct_hispanic_below_poverty,
                 pct_white_below_poverty_child, pct_white_below_poverty_adult, 
                 pct_native_below_poverty_child, pct_native_below_poverty_adult,
                 pct_hispanic_below_poverty_child, pct_hispanic_below_poverty_adult, 
                 pct_educ_less_hs_white, pct_educ_bachelor_white, 
                 pct_educ_less_hs_native, pct_educ_bachelor_native,
                 pct_educ_less_hs_hispanic, pct_educ_bachelor_hispanic, 
                 pct_umemployed_white, pct_umemployed_native, pct_umemployed_hispanic,
                 pct_disabled_white, pct_disabled_native, pct_disabled_hispanic,
                 pct_uninsured_white_19_64, pct_uninsured_native_19_64, pct_uninsured_hispanic_19_64)
  
  # Write out #
  write_rds(acs20_state_final, 
            file ="nm_acs20_state_final.rds")      
  
  # Turn the above into a function with a write out option -- then apply the function to the county  data
  # County #
  acs20_county <- get_acs(geography = "county", 
                          variables = acs_vars, 
                          year = 2020,
                          state = "CA", output="wide")
  
  # White Vector #
  white <- acs20_state_final %>%
    select(med_hh_inc_white,
           pct_hh_inc_white_100p,
           pct_hh_inc_white_125p,
           pct_snap_white,
           pct_white_below_poverty,
           pct_white_below_poverty_child,
           pct_white_below_poverty_adult,
           pct_educ_less_hs_white, 
           pct_educ_bachelor_white,
           pct_umemployed_white,
           pct_disabled_white,
           pct_uninsured_white_19_64)
  
  # Native Vector #
  native <- acs20_state_final %>%
    select(med_hh_inc_native, 
           pct_hh_inc_native_100p,
           pct_hh_inc_native_125p,
           pct_snap_native,
           pct_native_below_poverty,
           pct_native_below_poverty_child,
           pct_native_below_poverty_adult,
           pct_educ_less_hs_native,
           pct_educ_bachelor_native,
           pct_umemployed_native,
           pct_disabled_native,
           pct_uninsured_native_19_64) 
  
  # Hispanic Vector #
  hispanic <- acs20_state_final %>%
    select(med_hh_inc_hispanic,
           pct_hh_inc_hispanic_100p,
           pct_hh_inc_hispanic_125p,
           pct_snap_hispanic,
           pct_hispanic_below_poverty,
           pct_hispanic_below_poverty_child,
           pct_hispanic_below_poverty_adult,
           pct_educ_less_hs_hispanic, 
           pct_educ_bachelor_hispanic,
           pct_umemployed_hispanic,
           pct_disabled_hispanic,
           pct_uninsured_hispanic_19_64)
  
  # Combine Data #
  ses <- data.frame(White = round(t(white), 3),
                    Native = round(t(native),3),
                    Hispanic = round(t(hispanic),3)) %>%
    dplyr::mutate(White_NativeDiff = White - Native) %>%
    dplyr::mutate(White_HispanicDiff = White - Hispanic) %>%
    dplyr::mutate(Hispanic_NativeDiff = Hispanic - Native)
  
  # Recode Adjustments #
  ses$White[1] <- paste0("$",ses$White[1])
  ses$Native[1] <- paste0("$",ses$Native[1])
  ses$Hispanic[1] <- paste0("$",ses$Hispanic[1])
  ses$White_NativeDiff[1] <- paste0("$",ses$White_NativeDiff[1])
  ses$White_HispanicDiff[1] <- paste0("$",ses$White_HispanicDiff[1])
  ses$Hispanic_NativeDiff[1] <- paste0("$",ses$Hispanic_NativeDiff[1])
  
  # Table Labeling #
  colnames(ses) <- c("White", "Native", "Hispanic", "White - Native", "White - Hispanic", "Hispanic - Native")
  
  rownames(ses) <- c("Median Household Income",
                     "Pct. HH Income > $100K",
                     "Pct. HH Income > $125K",
                     "Pct. HH receiving SNAP",
                     "Pct. HH below poverty line",
                     "Pct. HH below poverty line, children",
                     "Pct. HH below poverty line, VAP",
                     "Pct. w/ Less than HS Diploma",
                     "Pct. w/ Bachelor's Degree or higher",
                     "Pct. Unemployed",
                     "Pct Disabled, ages 19-64",
                     "Pct. Uninsured, ages 19-64"
  )
  
  # Produce Table -- as an exmaple #
  reactable(ses,
            pagination = F,
            width = 700)
  
}

# Execute #
acs_factor5(vars = acs_vars,
            state = "CA")

```