---
title: "Factor 5 Analysis with eiFactor5"
subtitle: "Totality of Circumstances SES Disparities by Race/Ethnicity"
author: "Loren Collingwood"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Factor 5 Analysis with eiFactor5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Introduction

The `eiFactor5` package retrieves American Community Survey (ACS) data from
the U.S. Census Bureau and computes socioeconomic status (SES) indicators by
racial/ethnic group for Voting Rights Act Section 2 "totality of
circumstances" Factor 5 analysis.

Under the *Gingles* framework, Factor 5 of the "totality of circumstances"
test examines whether members of the minority group bear the effects of
discrimination in areas such as education, employment, and health, which
hinder their ability to participate effectively in the political process.

The package computes 12 SES indicators across up to five racial/ethnic groups
(White, Black, Hispanic, AAPI, and Native American), providing
publication-ready comparison tables, statistical significance testing, bar
charts, and choropleth maps.

## Setup

First, install the package and set your Census API key. You can obtain a free
key at [https://api.census.gov/data/key_signup.html](https://api.census.gov/data/key_signup.html).

```{r install}
# install.packages("devtools")
devtools::install_github("RPVote/eiFactor5")
```

```{r api-key}
library(eiFactor5)
library(tidycensus)

# Set your Census API key (only needed once per session)
census_api_key("YOUR_KEY_HERE")
```

## Available Indicators

The package computes 12 SES indicators:

```{r indicators, eval = TRUE}
library(eiFactor5)
knitr::kable(f5_indicators()[, c("id", "label", "acs_table")])
```

## Example 1: New Mexico Statewide Analysis

Compare Native American, Hispanic, and White populations across all New
Mexico counties.

### Fetch Data

```{r nm-fetch}
nm_dat <- f5_fetch(
  state = "NM",
  geography = "county",
  year = 2022,
  groups = c("white", "hispanic", "native")
)
head(nm_dat[, c("NAME", "pct_white", "pct_hispanic", "pct_native")])
```

### Comparison Table

```{r nm-table}
nm_table <- f5_table(
  nm_dat,
  ref_group = "white",
  compare_groups = c("hispanic", "native")
)
knitr::kable(nm_table, caption = "Factor 5 SES Comparison: New Mexico Counties")
```

### Statistical Tests

```{r nm-compare}
# Detailed pairwise comparison: White vs Native
nm_native <- f5_compare(nm_dat,
  ref_group = "white",
  compare_group = "native"
)
knitr::kable(
  nm_native[, c(
    "label", "ref_mean", "compare_mean",
    "diff", "t_stat", "p_value", "significant"
  )],
  digits = 3,
  caption = "White vs. Native American: Pairwise Tests"
)
```

### Bar Chart

```{r nm-plot, fig.width = 8, fig.height = 6}
f5_plot(nm_dat,
  ref_group = "white",
  compare_groups = c("hispanic", "native"),
  type = "bar"
)
```

### Dot Plot

```{r nm-dot, fig.width = 8, fig.height = 6}
f5_plot(nm_dat,
  ref_group = "white",
  compare_groups = c("hispanic", "native"),
  type = "dot"
)
```

## Example 2: Northern New Mexico Regional Analysis

Focus on northern New Mexico counties with significant Native American and
Hispanic populations: Santa Fe, Rio Arriba, Taos, San Juan, McKinley,
Sandoval, Los Alamos, and Colfax counties.

### Fetch Tract-Level Data

```{r north-nm-fetch}
north_nm_counties <- c("049", "039", "055", "045", "031", "043", "028", "007")

north_dat <- f5_fetch(
  state = "NM",
  county = north_nm_counties,
  geography = "tract",
  year = 2022,
  groups = c("white", "hispanic", "native"),
  geometry = TRUE
)

message("Retrieved ", nrow(north_dat), " tracts across 8 counties")
```

### Comparison Table

```{r north-table}
north_table <- f5_table(
  north_dat,
  ref_group = "white",
  compare_groups = c("hispanic", "native")
)
knitr::kable(north_table,
  caption = "Factor 5 SES Comparison: Northern NM Tracts"
)
```

### Choropleth Maps

Map the poverty rate for Native Americans across northern NM tracts:

```{r north-map-poverty, fig.width = 8, fig.height = 6}
f5_map(north_dat,
  indicator = "pct_below_poverty",
  group = "native",
  title = "Native American Poverty Rate\nNorthern New Mexico"
)
```

Map educational attainment for Hispanics:

```{r north-map-education, fig.width = 8, fig.height = 6}
f5_map(north_dat,
  indicator = "pct_less_hs",
  group = "hispanic",
  title = "Hispanic Pct. Less than HS Diploma\nNorthern New Mexico"
)
```

Map unemployment for White population as a comparison:

```{r north-map-unemp, fig.width = 8, fig.height = 6}
f5_map(north_dat,
  indicator = "pct_unemployed",
  group = "white",
  title = "White Unemployment Rate\nNorthern New Mexico"
)
```

### Bar Chart: Northern NM

```{r north-bar, fig.width = 8, fig.height = 6}
f5_plot(north_dat,
  ref_group = "white",
  compare_groups = c("hispanic", "native"),
  type = "bar"
)
```

## Example 3: Mississippi White vs. Black

A classic Factor 5 analysis comparing White and Black populations in
Mississippi at the county level.

```{r ms-fetch}
ms_dat <- f5_fetch(
  state = "MS",
  geography = "county",
  year = 2022,
  groups = c("white", "black")
)
```

```{r ms-table}
ms_table <- f5_table(ms_dat, ref_group = "white", compare_groups = "black")
knitr::kable(ms_table, caption = "Factor 5: Mississippi, White vs. Black")
```

```{r ms-plot, fig.width = 8, fig.height = 6}
f5_plot(ms_dat, ref_group = "white", compare_groups = "black")
```

## Example 4: National State-Level Comparison

Compare all five racial/ethnic groups at the state level across the entire
United States.

```{r national}
us_dat <- f5_fetch(
  geography = "state",
  year = 2022,
  groups = c("white", "black", "hispanic", "aapi", "native")
)

us_table <- f5_table(
  us_dat,
  ref_group = "white",
  compare_groups = c("black", "hispanic", "aapi", "native")
)
knitr::kable(us_table, caption = "Factor 5: National, State-Level")
```

## Interpreting Results

In Factor 5 analysis for VRA Section 2 litigation:

- **Income indicators**: Lower median household income and lower rates of
  high-income households among minority groups indicate economic disparities.
- **Poverty indicators**: Higher poverty rates (overall, children, adults)
  for minority groups show the effects of discrimination on economic status.
- **Education indicators**: Higher rates of less-than-HS education and lower
  rates of bachelor's degrees indicate educational disparities.
- **Employment**: Higher unemployment rates among minority groups.
- **Disability & Health**: Higher disability rates and lack of health
  insurance indicate health-related disparities.
- **Statistical significance**: The t-test p-values indicate whether
  observed differences are statistically significant (p < 0.05).

These disparities, when present, support the argument that minority group
members bear the effects of discrimination in areas that hinder effective
political participation.

## Citation

If you use this package in academic work, please cite:

> Collingwood, L. (2026). eiFactor5: Totality of Circumstances Factor 5
> Analysis Using Census ACS Data. R package version 1.0.0.
> https://github.com/RPVote/eiFactor5
